\documentclass[11pt]{res} % Use the res.cls style, the font size can be changed to 11pt or 12pt here
\usepackage{helvet} % Default font is the helvetica postscript font
%\usepackage{newcent} % To change the default font to the new century schoolbook postscript font uncomment this line and comment the one above
\usepackage{hyperref,textcomp,fontawesome,fancyhdr, hanging}
\newsectionwidth{0pt} % Stops section indenting
\begin{document}
%----------------------------------------------------------------------------------------
%	YOUR NAME AND ADDRESS(ES) SECTION
%----------------------------------------------------------------------------------------
\name{DAVID JOHN BAKER\\ \\ }
%----------------------------------------------------------------------------------------
\begin{resume}
%------------------------------------------------------------==--------------
%	EDUCATION 
%----------------------------------------------------------------------------

%------------------------------------------------------------==--------------
%	EDUCATION
%----------------------------------------------------------------------------
\section{EDUCATION} 
\vspace{8pt} % Gap between title and text
Ph.D., Music Theory; Minor in Cognitive and Brain Sciences  \hfill August, 2019  \\
Louisiana State University, Baton Rouge, Louisiana, USA \\ \\
\-\hspace{1cm} \emph{Modeling Melodic Dictation} \\
\-\hspace{1cm} Demonstrated how tools from computational musicology and cognitive \\ \-\hspace{1cm} psychology can inform research on melodic memory via melodic dictation

MSc., Music, Mind and Brain \hfill September, 2014\\
Goldsmiths, University of London, England

B.M., Instrumental Performance (Trumpet) \hfill May, 2012 \\ 
Baldwin Wallace University, Conservatory of Music, Berea, Ohio, USA 

\section{CAREER}
\vspace{8pt} % Gap between title and text

\textbf{Postdoctoral Research Associate} \hfill February 2022 -- \textit{Current}
\\Institute of Logic, Language and Computation\\ \textit{University of Amsterdam}

\textbf{Postdoctoral Research Associate} \hfill May 2021 -- January 2022 
\\Department of Psychology\\ \textit{Goldsmiths, University of London}

\textbf{Senior Research Associate} \hfill September 2020 -- June 2021 
\\Department of Computing\\ \textit{Goldsmiths, University of London}

\textbf{Lead Instructor, Data Science} \hfill September 2019 -- June 2020 \\
Flatiron School, \\\textit{WeWork}

%----------------------------------------------------------------------------------------
%	PUBLICATIONS SECTION (APA)
%----------------------------------------------------------------------------------------
\section{PUBLICATIONS} 

\subsubsection{\centerline{Articles}}
\begin{hangparas}{.25in}{1}

\textbf{Baker, D}. (2021). The \textit{MeloSol} Corpus. \textit{Empirical Musicology Review} \href{https://psyarxiv.com/cmwr6}{[Preprint via PsyArXiv]}

Brown, J., Tan, D., \& \textbf{Baker, D.} (2021) The perceptual attraction of pre-dominant chords. \textit{Music Perception}. \href{https://psyarxiv.com/8abys}{[Preprint via PsyArXiv]}

Vuvan, D. T., Simon, E., \textbf{Baker, D.}, Monzingo, E., \& Elliott, E. M. (2020). Musical Training Mediates the Relation Between Working Memory Capacity and Preference for Musical Complexity. \textit{Memory and Cognition}. https://doi.org/10.31234/osf.io/9fe8n 

\textbf{Baker, D.}, Ventura, J., Calamia, M., Shanahan, D., Elliott, E. (2018). Examining Musical Sophistication: A replication and theoretical commenatry on the Goldsmiths Musical Sophistication Index. \textit{Musicae Scientiae}. Vol. 24(4) 411 $-$ 429 https://doi.org/10.1177/1029864918811879 

Akkermans, J., Schapiro, R., M\"{u}llensiefen, D., Jakubowski, K., Shanahan, D., \textbf{Baker, D}.,  Busch, V., Lothwesen, K., Elvers, K., Fischinger, T.,  Schlemmer, K. \& Frieler, K. (2018). Decoding emotions in expressive music performances: A multi-lab replication and extension study. \textit{Cognition and Emotion}, \textit{33}(6). doi:10.1080/02699931.2018.1541312 

\textbf{Baker, D.} and M\"{u}llensiefen D. (2017). Perception of Leitmoitves in Richard Wagner's \textit{Der Ring des Nibelungen}. Frontiers in Psychology: Cognition, Special Issue on Bridging Music Informatics with Music Cognition. \href{http://journal.frontiersin.org/article/10.3389/fpsyg.2017.00662/full}{[https://doi.org/10.3389/fpsyg.2017.00662]}

\end{hangparas}

%Book Chapters
\subsubsection{\centerline{Book Chapters}}

\begin{hangparas}{.25in}{1}
Shanahan, D. \& \textbf{Baker, D.} (\textit{forthcoming} 2022). The Corpus as Proxy for Perception and Cognition of Music. In Shanahan, Quinn, Burgoyne (Eds.), \textit{The Oxford Handbook of Musical Corpus Studies}. Oxford University Press.

\textbf{Baker, D.} (2021). Understanding Melodic Dictation via Experimental Methods. In P. Fleet \& K. Cleland (Eds.), \textit{Routledge Companion to Aural Training in Music Education} (pp. 414-423). Milton Park, Abingdon, Oxon: Routledge.

\textbf{Baker, D.} and Shanahan, D. (2018). Examining Fixed and Relative Measurements of Similarity through Jazz Melodies. In \textit{Scholarly Approaches to Mathematical Music Theory: Algebra and Combinatorics, Geometry, Topology, and Graph Theory, Discrete Fourier Transform and Distance Measures for Music}.

M\"{u}llensiefen, D., \textbf{Baker, D.}, Rhodes, C,. Crawford, T,. Dreyfus, L. (2016). Recognition of leitmotives in Richard Wagner's music: chroma distance and listener expertise. In Springer (Ed.) \textit{Analysis of Large and Complex Data}. 

M\"{u}llensiefen, D., \textbf{Baker, D}. (2015) Music in Advertising: Testing What Works (2015) Audio Branding Academy Yearbook 2015.
\end{hangparas}

% Conference Proceedings
% Book Reviews
\subsubsection{\centerline{Reviews and Editorials}}

\begin{hangparas}{.25in}{1}
\textbf{Baker, D.}, Belfi, A., Creel, S., Grahn, J., Hannon, E., Loui, P.,  Margulis, E., Schachner, A., Schutz, M., Shanahan, D., Vuvan, D. (2020). Embracing Anti-Racist Practices in the Music Perception and Cognition Community. \emph{Music Perception}. \textit{38}(2). pp. 103–-105.\\ https://doi.org/10.1525/mp.2020.38.2.103 [Editorial]\\ 

\textbf{Baker, D}. (2018) ``Coughing and Clapping", in \emph{Empirical Musicology Review }, Vol 13, No. (3-4), pp. 164-165. [Book Review] \\

\textbf{Baker, D}. (2015)  "Unlocking the Mysteries of Your Brain, Dr. Daniel Levitin Public Lecture", in \emph{Psychomusicology: Music, Mind, and Brain}, Vol 25, No.4, pp. 455-456. [Public Lecture Review] 
\end{hangparas}

\subsubsection{\centerline{Select Conference Proceedings}}

\begin{hangparas}{.25in}{1}

Krause, A. E., \textbf{ Baker, D. J.}, Groarke, J., Pereira, A. I., Liew, K., Anglada-Tort, M., \& Steffens, J. (2021). A cross‐cultural investigation of music listening practices: The influence of country latitude and seasons on music preference. Paper presented at the 16th International Conference on Music Perception and Cognition (ICMPC)/ 11th triennial conference of the European Society for the Cognitive Sciences of Music (ESCOM).

Weigl, D., Goebl, W., \textbf{Baker, D.}, Crawford, T., Zubani, F., Gkiokas, A.,  Paez, N., Porter, A. and Santos P. (July, 2021) Notes on the Music: A social data infrastructure for music annotation. Digital Libraries for Musicology. ACM (Association for Computing Machinery). doi: 10.1145/3469017

\textbf{Baker, D.}, Elliott, E., Shanahan, D., Ventura, J. Monzingo, E., Ritter, B., \& Young, C. (2018) Explaining Objective and Subjective Aspects of Musical Sophistication: Insights from General Fluid Intelligence and Working Memory. \textit{Proceedings of 2018 International Conference on Music Perception and Cognition.}

Shanahan, D., Elliott, E., \textbf{Baker, D.}, Ventura, J., Monzingo, E., Holt, H., \& Keller, H. (2018) Dissecting the Effects of Working Memory, General Fluid Intelligence,
 and Socio-Economic Status on Musical Sophistication. \textit{Proceedings of 2018 International Conference on Music Perception and Cognition.}
 
\textbf{Baker, D.}, Monzingo, E., \& Shanahan, D. (2018) Modeling Aural Skills Dictation. \textit{Proceedings of 2018 International Conference on Music Perception and Cognition.} 

%Monzingo, E., \textbf{Baker, D.}, \& Shanahan. D. (2018) The Relationships Between Genre Preference, Aural Skills, and Tonal Working Memory.\textit{Proceedings of 2018 International Conference on Music Perception and Cognition.} 

%Monzingo, E., Shanahan D., Marasco, A., Elliott, E., \textbf{Baker, D.}, Davis, D., \& Albrecht, J. The Effects of Melodic Contagions in the Oral Transmission of Melodies. \textit{Proceedings of 2018 International Conference on Music Perception and Cognition.} 

\textbf{Baker, D.}, Trahan, T., M\"{u}llensiefen, D. (2016) Measuring Music To Brand Personality: A Semantic Differential Tool for Measuring Emotional Space. \textit{Proceedings of 2016 International Conference on Music Perception and Cognition.}

\textbf{Baker, D.}, Rosado, A, Shanahan, E., Shanahan, D. (2016) The Interaction of Schema-Driven Gestures and Instrumental Affordances in Bebop Improvisations. \textit{Proceedings of 2016 International Conference on Music Perception and Cognition.}
  
%Blust, A., \textbf{Baker, D.}, Richard, K., Shanahan, D. (2016) Music, Animacy, and Rubato: What makes music sound human? \textit{Proceedings of 2016 International Conference on Music Perception and Cognition.}

Berhdal, E., Blandino, M., \textbf{Baker, D.}, Shanahan, D. (2016). An Approach for Using Information Theory to Investigate Continuous Control of Analog Sensors by Humans. Audio Mostly. Norrköping, Sweden. [Conference Proceedings Paper]

\textbf{Baker, D}., Rindfleisch, C., M\"{u}llensiefen, D. (2015) Parsifal and the effect of narrative on unconscious arousal. \textit{Proceedings of 2015 European Soceity of Cognitive Sciences of Music}

M\"{u}llensiefen, D., \textbf{Baker, D}., Lewis, R., Rhodes, C., Fields, B., and Crawford, T. (2014) Multi-modal Musical Performance Capture. In: \emph{Digital Music Research Network (DRM+9)}. London, United Kingdom. [Conference/Workshop Item]
\end{hangparas}

\subsubsection{\centerline{Other Publications}}

Lin, X., \textbf{Baker D.}, Assefa, S., Tarkhnishvili, N. (2019) Beyond Age and Income: Encouraging saving behaviours. Toynbee Hall. \href{https://www.toynbeehall.org.uk/wp-content/uploads/2019/09/Beyond-Age-and-Income-web.pdf}{[Research Report]}

% In Submission (Yet to Have) If have journal title
\subsubsection{\centerline{Manuscripts}}

\subsubsection{Under Review}

\begin{hangparas}{.25in}{1}

Ma, Y., \textbf{Baker, D.}, Vukovics. K., Davis, C.J, Elliott, E., (July, 2021). Generalizing the Effect of  Lyrics on Emotion Ratings. https://psyarxiv.com/5ku43

\textbf{Baker, D.}, Elliott, E., Ventura, J., Shanahan, D. (July, 2019). The Prediction of Working Memory Capacity by Music Training and Aptitudes: The Importance of Non-Verbal Intelligence and Tonal Stimuli.

\end{hangparas}

\subsubsection{Revising after Rejection}

\begin{hangparas}{.25in}{1}
\textbf{Baker, D}. (\textit{in preparation}) Frequently Occurring Musical Patterns are Easier to Recall.\\ https://osf.io/3rjzu/ 
\end{hangparas}

\subsubsection{In Preparation}

\begin{hangparas}{.25in}{1}

\textbf{Baker, D}. (\textit{in preparation}) A Computational Model of Melodic Dictation. \\ \textit{Invited to Submit to Special Issue of Music \& Science Explaining music with AI: Advancing the scientific understanding of music through computation}

\textbf{Baker, D.} and M\"{u}llensiefen, D. Additive or Emergent? (\textit{in preparation}) Pairing Music and Visual Scenes at Scale.

\textbf{Baker, D.} and M\"{u}llensiefen, D. (\textit{in preparation}) What does it mean for an audio logo to be memorable? 

% Matching Pairs Methodology 
% Games Review 

\end{hangparas}

\newpage


\section{TEACHING} 
\vspace{12pt} % Gap between title and text


\subsection{\centerline{Advising}}

\textbf{Daily Supervisor} \hfill February 2022 -- \textit{Current}\\
% Where
University of Amsterdam \\
% Magnitude
Daily supervisor for PhD candidate Jiaxin Li:\\ 
\textit{What is the importance of spectral information in music recognition}\\ 

\textbf{Undergraduate Dissertation Supervisor} \hfill Spring 2022\\
% Where
University of Cambridge\\
% Magnitude
Co-advised on dissertation for Kirsty Ryall \\\textit{Music and Dyslexia: An investigation into strategies for musical memory} 
% One Line Description

\textbf{Flatiron School} \hfill  Autumn 2019 -- June 2020\\
Flatiron School Data Science Bootcamp \\ 
Supervised final data science portfolio projects\\
\textit{Lead Instructor}, In Person, Online
\subsection{\centerline{Classroom Teaching}}

\textbf{Guest Lecturer} \hfill Winter 2022\\
% Where
Goldsmiths, University of London \\
% Magnitude
Guest lectured on graduate classes on timbre analysis the peer review process\\


\textbf{Guest Lecturer} \hfill Spring 2022\\
% Where
University of Cambridge\\
% Magnitude
Delivered three lectures at Masters level on music, psychology, and emotion \\
% One Line Description

\textbf{Computational Musicology} \hfill Spring 2022\\
% Where
University of Amsterdam \\
% Magnitude
Assisted in labs, grading, tutorials for 70+ course\\
% One Line Description
Hybrid delivery of topic for music and AI undergraduates\\
% Role 
\textit{Teaching Assistant}

\textbf{Issues in Music and Science} \hfill Winter 2020\\
% Where
Humboldt-Universit{\"a}ät zu Berlin, Germany\\
% Magnitude
Delivered 16 lecture course for undergraduates\\
% One Line Description
Introduction to study of Music and Science\\
% Role 
\textit{Instructor of Record}, Online

\textbf{Lead Instructor, Data Science} \hfill September 2019 -- June 2020\\
Flatiron School x WeWork, London\\
Delivered daily lectures, advised projects, developed curricula\\
Vocational Coding Bootcamp\\
\textit{Lead Instructor}, In Person and Online 

\textbf{Multivariate Statistics} \hfill  Spring, 2018\\
Louisiana State University\\
Assisted with weekly lectures\\
Advanced Statistics for Graduate Students in Psychology\\
\textit{Graduate Teaching Assistant}, In Person

\textbf{Intermediate Statistics} \hfill  Fall, 2017\\
Louisiana State University\\
Assisted with weekly lectures\\
Intermediate Statistics for Students in Psychology\\
\textit{Graduate Teaching Assistant}, In Person

\textbf{Foundations of Music Study} \hfill  Fall, 2016\\
Louisiana State University\\
Prepared and delivered 15 Week Course\\
Remedial Music Theory Course for Undergraduates\\
\textit{Instructor of Record}, In Person

\textbf{Aural Skills IV} \hfill  Spring 2016, 2017\\
Louisiana State University\\
Prepared and delivered 15 Week Lab\\
Chromatic and Post Tonal Aural Skills for Undergraduates\\
\textit{Instructor of Record}, In Person

\textbf{Aural Skills III} \hfill  Autumn 2015, 2016\\
Louisiana State University \\ 
Prepared and delivered 15 Week Lab\\
Chromatic Aural Skills for Undergraduates\\
\textit{Instructor of Record}, In Person


\section{SERVICE}

\subsection{\centerline{Academic}}
\textbf{Chair, Anti-Racism and Equity Committee} \hfill 2022 -- present \\
Society for Music Perception and Cognition \hfill 


\textbf{Consortium on Musicality and Genetics} \hfill June 2020 -- Current \\
Assisted Henkjan Honing, Reyna Gordon, and Simon Fisher in \\
organising two events to initiated consortium on musicality\\
and genetics

\textbf{Digital Libraries for Musicology, 2022} \hfill January 2020 -- July 2022 \\
Proceedings Chair

\textbf{Anti-Racism and Equity Committee} \hfill 2020 -- present \\
Society for Music Perception and Cognition \hfill 

\textbf{Mentor, WiMIR Mentoring Program} \hfill 2020 -- 2021 \\
International Society for Music Information Retrieval \hfill 

\textbf{Trainee Member, Executive Board} \hfill 2019 -- 2020 \\
Society for Music Perception and Cognition \hfill 
\begin{itemize} \itemsep -2pt % Reduce space between items
\item[--] Organized trainee events at conference including Faculty-Student lunch, Applying to Graduate School Panel, Early Career Session Panel, and Student Meet-and-Greet
\item[--] Duties to assist and advise the President, Secretary, Treasurer, and President Elect in their deliberations and their duties, and in general shall see to the welfare of SMPC 
\item[--] Represented the views of student members of SMPC 
\item[--] Served on Election Committees and Anti-Racism Committee
\end{itemize}

%\subsection{\centerline{Peer Review}}
\textbf{Ad Hoc Peer Reviewer } \hfill 2018 -- \textit{present}
\begin{itemize} \itemsep -2pt % Reduce space between items
\item[--] \textit{Music Perception
\item[--] Annals of the New York Academy of Sciences
\item[--] Music and Science
\item[--] Musicae Scientiae
\item[--] Psychology of Music
\item[--] SysMus} Conference Series 
\end{itemize}

\subsection{\centerline{Non Academic}}
\textbf{Research and Evaluation Resident} \hfill June 2018 -- March 2019 \\
Toynbee Hall, London, England \hfill 
\begin{itemize} \itemsep -2pt % Reduce space between items
\item[--] Used a Participatory Action Research research with East London communities
\item[--] Topics researched included financial savings, mental health support for advice users, private renting, poverty premium, and support for young people
\item[--] Organized Datathon partnering community organizations and data scientists for \#DataForGood event
\end{itemize}

%\textbf{LSU Summer Institute on the Future of Graduate Studies} \hfill May, 2018 \\
%Baton Rouge, Louisiana \hfill 
%\begin{itemize} \itemsep -2pt % Reduce space between items
%\item Served as on advisory committee/think tank with both students and faculty for LSU Graduate School 
%\item Met daily for 3 weeks to discuss LSU's commitment to AltAc and Career Diversity
%\item Created draft of mentoring document proposed to be used across campus
%\end{itemize}

%\textbf{Student Representative for Search for Dean } \hfill Spring, 2012 \\
%Berea, Ohio \hfill 
%\begin{itemize} \itemsep -2pt % Reduce space between items
%\item Served on committee to select Dean for Baldwin Wallace Conservatory of Music 
%\item Organized and led all Student--Candidate symposia  
%\end{itemize}


\section{Awards and Funding}

\subsubsection{\centerline{Notable Honors}}

\textbf{Honorable Mention} \hfill  April, 2020\\
Josephine A. Roberts LSU Alumni Association \\
2019 Distinguished Dissertation Award in Arts, Humanities, and Social Sciences\\
The Graduate Faculty\\
Louisiana State University\\
\textit{Campus Wide Competition}

\textbf{LSU Dissertation Year Fellowship} \hfill 2018 -- 2019\\
The Graduate School \hfill \$18,000\\
Louisiana State University\\
\textit{Annually Awarded to Single Dissertation in Arts, Humanities, and Social Sciences}\\

\textbf{National Science Foundation} \hfill Fall, 2017 \\
National Science Foundation \hfill \$2,000 \\
Valencia, Spain \\
Travel Grant from NSF to attend \textit{This Is Your Brain On Art} Conference\\

\section{PRESENTATIONS}


\begin{hangparas}{.25in}{1}
\subsection{\centerline{Invited Talks}}

\textbf{Baker, D.} (May, 2022). Considering Plan D: Data Science after Academia. \emph{AMPlify Your Research Career Series}. Australian Music and Psychology Society. 

\textbf{Baker, D.} (October, 2021). Frequently Occurring Melodic Patterns are Easier to Recall. \emph{Computational Audition and Perception Group}. Max Planck Institute for Empirical Aesthetics. 

\textbf{Baker, D.} (February, 2021) Career Talk for Introduction to Music and Science. \emph{Faculty of Music}. University of Cambridge. 

\textbf{Baker, D.} (January, 2021) Turning Your Values in to Value: Getting a Job in Industry. \emph{Psychology Department}. Goldsmiths, University of London, Online Workshop for Graduate Students and Post-Docs. 

\textbf{Baker, D.} (February, 2020) Memory for Melodies. Music Cognition, Quinnipiac University. New Haven, Connecticut. \textit{Skype Lecture}

\textbf{Baker, D.} (March, 2019) Music Cognition and Music Theory. Analytic Techniques in Music Theory, Louisiana State University. Baton Rouge, Louisiana. \textit{Skype Lecture}

\textbf{Baker, D.} (November, 2018) Modeling Melodic Dictation. Research Seminar: Computing \& Communications Department, The Open University. Milton Keynes, England.
\end{hangparas}


\newpage

\subsection{\centerline{Workshops and Symposia}}
\begin{hangparas}{.25in}{1}

Vuvan, D., Belfi, A., Shanahan D., \textbf{Baker, D.}, Loui, P.  (March, 2021)  Town hall on anti-racism in music cognition. Future Directions of Music Cognition. Online Town Hall. \textit{Presented on History of Science, Racism, and Music.}

\textbf{Baker, D.} (September, 2020) Turning Your Values in to Value: Getting a Job in Industry. SysMus 2020. University of York, Online Workshop. 

\textbf{Baker, D.}, Kragness, H., Loui, P., Slevc, R., Upham, F., Vuvan, D. (May, 2019). Symposium on Open Science. Society for Music Perception and Cognition. New York, New York. [Symposium] 
\end{hangparas}

\section{DATA SCIENCE AND SOFTWARE DEVELOPMENT}

\vspace{1cm}
%\subsection{\centerline{Software Development}}

%\textbf{Software Developer} \hfill May 2021 -- August 2021 
%\\Computational Audition and Perception Group\\ \textit{Max Planck Institute for Empirical Aesthetics}

\subsection{\centerline{Consultancy Projects}}

\textbf{End Point Assessor} \hfill  Autumn 2021\\
London, England\\
Acted as End Point Assessor for Masters in Data Science Project\\
-- Ongoing \\
\textit{Doran Scott Williams}

\textbf{Scientist} \hfill  Autumn 2021\\
London, England\\
Assisted in testing of audio assets for international investment services company\\
-- Ongoing \\
\textit{Massive Music}

\textbf{Scientist} \hfill  Winter 2020\\
London, England\\
Assisted in creation of audio identity for international pharmaceutical client\\
-- Ongoing \\
\textit{Massive Music}

\textbf{Scientist} \hfill  March 2018--April 2019\\
London, England\\
Developed music for modern traveler\\
Press Coverage in Forbes, easyJet Traveller, b{\o}rsen (DK)\\
\textit{Soundscape Agency, Citizen M Hotels, Erased Tapes, Bose}

\textbf{Data Scientist} \hfill  March 2018--April 2019\\
New York City, USA\\
Developed tool for detecting audio logo uniqueness\\
Advised on statistical implementations platform\\
\textit{Veritonic, Inc.}

\textbf{Project Consultant} \hfill  March 2018--April 2019\\
London, England\\
Created tool to match brand personality to perceived emotion\\
Prototype published in 2016 ICMPC Proceedings\\
Research served as prototype for Soundout's Brand Match Tool \\
\textit{Soundout}

\textbf{Presenter} \hfill  March 2018--April 2019\\
Berlin, Germany\\
Co-lead half-day workshop on academic research in audio branding\\
Focused on brand-personality matching, q methodology, analyzing physiological data\\
\textit{Audio Branding Academy}

\subsection{\centerline{Teaching and Education}}

\textbf{Baker, D.} (May, 2020) Crash Course in Clustering Algorithms. Flatiron School. London, England. \textit{Zoom Lecture} \href{https://www.youtube.com/watch?v=EKTVTfAXVIo&feature=emb_logo}{Link to Talk Here}

\textbf{Baker, D.} (March, 2020) The Science of Netflix: How Recommendation Systems Work. Online Meet-Up. Flatiron School. London, England. \textit{Zoom Lecture} \href{https://www.youtube.com/watch?v=xkMqgWHn36w&t=5s}{Link to Talk Here}

\textbf{Baker, D.} (2019) haRnessing The Open Source Community to Help Local Communities. EARL London Conference. September 10--12th [10 Minute \#data4good Flash Talk]

\subsection{\centerline{Continuing Professional Development}}


\begin{itemize}
    \item[--] RStudio Certified \texttt{tidyverse} Instructor \hfill Spring, 2020
    \item[--] Attended Frank Harrell's Regression Modeling Strategies Short Course \hfill  Spring 2020
\end{itemize}


 
\end{resume} 
\end{document}