


%\subsection{\centerline{Academic Textbook Contributions}}

%\textbf{MUTOR: MUsic Technology Online Repository} \hfill  Fall, 2020\\
%$E-Learning Consortium Hamburg\\
%Edited and Contributed to Online Textbook\\
%Music Perception and Cognition\\
%\textit{Contributor}


\subsection{\centerline{Conference Presentations}}

\begin{hangparas}{.25in}{1}


HOLDER DGM Semantic 

HOLDER Online Games Abstract 

HOLDER SMPC Semantic 

HOLDER SMPC RPAP 

HOLDER. P2P RP AP 


Krause, A. E., \textbf{ Baker, D. J.}, Groarke, J., Pereira, A. I., Liew, K., Anglada-Tort, M., & Steffens, J. (2021). A cross‐cultural investigation of music listening practices: The influence of country latitude and seasons on music preference. Paper presented at the 16th International Conference on Music Perception and Cognition (ICMPC)/ 11th triennial conference of the European Society for the Cognitive Sciences of Music (ESCOM).

\textbf{Baker, D.} (August, 2019). Modeling the Limits of Musical Memory. CogMir19. New York, New York. \href{https://www.youtube.com/watch?v=T6G4m6_xFrc}{[Video]} 

\textbf{Baker, D.} (August, 2019). What is happening in a student’s mind when they perform melodic dictation?. Society for Music Perception and Cognition. New York, New York.  [Talk] 

\textbf{Baker, D.} (May, 2019). The Frequency Facilitation Hypothesis. Society for Music Perception and Cognition. New York, New York. [Poster] 

Ma, Y., Elliott, E., \textbf{Baker, D}., Davis, C., Vukovics, K. (May, 2019). Lyrics and Emotion in Songs: A Conceptual Replication Study of Ali and Peynircioglu, 2006. Society for Music Perception and Cognition. New York, New York. [Poster] 

Vukovics, K., Elliott E., Ma, Y., \textbf{ Baker, D.} (May, 2019). Does Musical Training Protect Against Auditory Distractions?. Society for Music Perception and Cognition. New York, New York. [Poster] 

Simon, E., \textbf{Baker D.}, Monzingo, M., Elliott, E., & Vuvan, D. (May, 2019). Musical Training Mediates the Relation Between Auditory Working Memory and Preference for Musical Complexity. Society for Music Perception and Cognition. New York, New York. [Poster]

\textbf{Baker, D.} (May, 2019). What is going on in someone’s head when they do melodic dictation?. Pedagogy into Practice. Santa Barbara, California.  [Read Paper] 

\textbf{Baker, D.}(May, 2019). What is going on in someone’s head when they do melodic dictation?. Music Theory Midwest, Cincinnati, Ohio. [Read Paper] 

\textbf{Baker, D.}(April, 2019). The Frequency Facilitation Hypothesis. Again \& Again
Musical Repetition in Aesthetics, Analysis and Experience. London, England [Read Paper] 

\textbf{Baker, D.}(March, 2019). What is going on in someone’s head when they do melodic dictation? SEMPRE Graduate Conference. Cambridge, England. [Lightening Talk] 

\textbf{Baker, D.}, Elliott, E., Shanahan, D., Ventura, J. Monzingo, E., Ritter, B., \& Young, C. (July, 2018). Explaining Objective and Subjective Aspects of Musical Sophistication:
Insights from General Fluid Intelligence and Working Memory. Proceedings of 2018 International Conference on Music Perception and Cognition. [Short Talk] 

\textbf{Baker, D.}, Monzingo, E., \& Shanahan, D. (July, 2018). Modeling Aural Skills Dictation. Proceedings of 2016 International Conference on Music Perception and Cognition. [Conference Poster]

Gran, J., \textbf{Baker, D.} (March, 2018). Root Interval Schemas in Rock Music. Music Theory South Central, University of Southern Mississippi. [Read Paper, Slides] 

\textbf{Baker, D}. (March, 2018). Who counts as a Musician?, Music and Public Discourse, Columbia, South Carolina. \href{ https://youtu.be/U-iDi4M6BV8}{ [Video] }

\end{hangparas}
% Whole Section on Data Science 



\vspace{-.25cm}
\subsubsection{\centerline{Research}}
Visiting PhD Student, Queen Mary, University of London, July 2016  \hfill   \pounds 500\\
Visiting PhD Student, Transforming Musicology, June 2016 \hfill     \pounds 2,000\\
Research and Administrative Assistant at Transforming Musicology, Fall 2015 \hfill  \pounds 5,000\\
\vspace{-1cm}
\subsubsection{\centerline{Travel}}
SEMPRE Travel Award, April 2018 \hfill \texteuro 130\\
LSU Graduate Student Association Travel Award, South Carolina, March 2018 \hfill \$200 \\
LSU School of Music Award Travel Award, South Carolina, February 2018 \hfill      \$250 \\ 
LSU School of Music Travel Award, San Diego, July 2017 	\hfill    \$750\\
SMPC Student Travel Award, San Diego, July 2017	\hfill	    \$500\\
LSU School of Music Travel Award, Missouri, November 2016 \hfill	   \$500\\
Travel Bursary from Deutsche Gesellschaft f\"{u}r Musikpsychologie, August 2015  \hfill  \texteuro 100\\
\vspace{-1cm}
\subsubsection{\centerline{Education and Scholarships}}
LSU Summer Institute on Future of Graduate Studies, May 2018 \hfill \$3,500\\
LSU Department of Psychology Graduate Assistantship (1 Year), Autumn 2017 -- Spring 2018 \hfill \$13,000\\
LSU School of Music Graduate Assistantship (3 Years), Autumn 2015 -- Spring 2017 \hfill \$33,000\\
Goldsmiths International Postgraduate Scholarship, September 2014--September 2015 \hfill  \pounds 5,000\\
Baldwin Wallace University President’s Scholarship \hfill  \$48,000\\
Baldwin Wallace University Director’s Scholarship \hfill \$4,000\\
Baldwin Wallace Griffiths Scholarship \hfill \$1,000\\
Baldwin Wallace University Gloria B. Ewing Scholarship \hfill \$1,500\\